|

### 2021-12-02 03-Chp-Systematic-Review-Methods.Rmd
End of day:

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading.)

@@

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but  report relevant unpublished analyses. As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

Given the size of the review, I have seperated the methods and results into two chapters for ease of reading. This chapter details the methodology used, while CHapter \@ref(sys-rev-results-heading) presents the results of the review.

@@

I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides). I also aimed to include studies examining the effect of treatments that modify blood lipid levels, such as statins or fibrates, as a source of indirect evidence.

Eligible study designs were randomized controlled trials, non-randomized studies of exposures, non-randomised studies of  , longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits were placed on the sample size of included studies.

Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.

<!-- COMMENT Isn’t more true to say it was assumed that a health care professional had made the diagnosis (unlikely to use specific criteria) -->

@@

<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->

@@

Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status, were eligible for inclusion. Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g. MoCA score) without an attempt to map these scores to ordinal groups (e.g. no dementia/dementia). Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

When searching the bibliographic databases, study design filters were employed to try and reduce the screening load. To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"[@greenhalgh2005; @wohlin2014]).

@@

Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]

The criteria against which records were assessed for eligibility are presented above.

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of less than .9), a larger proportion of records would have been dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.

@@

Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]

@@

A key aim of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis). To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.

@@

This move was prompted by an unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools. <!-- TODO CITATION NEEDED --> As part of this shift, the focus shifted from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order. <!-- TODO CITATION NEEDED -->
Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.  For example, a study may report on the efficacy of an intervention at six months and two years follow-up. In this case, missing outcome data that are not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.

@@

Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result. Acceptable judgements for each domain include: "low risk", "some concerns", "high risk". Each of the five domains contains a series of signaling questions or prompts which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result. Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “low risk”, “moderate risk”, “serious risk” and “critical risk”. In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial. Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level. The motivation using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification. Acceptable judgements for each of the 5 domains in the tool included "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level. This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.

@@

Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading). Analysis are presented seperately for each dementia type of interest.

@@

I used a random-effects model in all meta-analysis presented in this chapter.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.

Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:

@@

Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels. This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.

@@

I took a two-stage dose-response meta-analysis approach, where study-specific trends are estimated before being pooled acrosss studies.[@greenland1992] To estimate within-study trends, a restricted cubic spline model was fitted within each to allow for a non-linear relationship between lipid levels and dementia, for example a U or J-shaped relationship, where low and high levels of a lipid fraction can have different effects versus the "normal" reference dose.[@durrleman1989;@liu2009] <!-- TODO CITATION NEEDED --> 
Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

Restricted cubic spline models use "knots" to create separate the data into subsets or "windows", in which the trend is modelled. Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]

@@

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.

@@

* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and treatments for lowering blood lipids.

* I have highlighted how this review will make use of preprinted literature, using the research tool introduced in the preceding chapter (Chapter \ref(sys-rev-tools-heading)).

* In the following chapter, I presented the results of this comprehensive systematic review and detail how the identified evidence is used throughout the remainder of the thesis.

>>>>

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).

@@

Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses. As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).

Given the size of the review, I have separated the methods and results into two chapters for ease of reading. This chapter details the methodology used, while Chapter \@ref(sys-rev-results-heading) presents the results.

@@

I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides). I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence. LRA are treatments used to modify blood lipids levels, and common examples include statins, fibrates, and ezetimibe.

Eligible study designs were randomized controlled trials of LRA, cohort studies examining blood lipids or LRA, and genetic instrumental variable studies (more commonly known as Mendelian randomization studies) examining the effect of genetically increased/decreased blood lipid levels.

Eligible studies screened participants for dementia at baseline and excluded any prevalent cases. Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline. Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate. No limits were placed on the sample size of included studies. Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering used when entering the outcome into the EHR.

@@

@@

Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion. Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g. MoCA score) without an attempt to map these scores to ordinal groups (e.g. no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.

Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) were excluded. Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded. For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated. Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet. Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.

@@

I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records"). The following databases were searched in June 2019 from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases). The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed. A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy). <!-- TODO Need to actually attach each search strategy. Should be able to loop through search strategy results. -->

@@

When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try and reduce the screening load. To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.

@@

Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. In addition, the abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand. <!-- TODO how were these searched? Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing").[@greenhalgh2005; @wohlin2014]

@@

Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records I identified as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated issues with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.

@@

Data extraction was performed using a piloted data extraction form. Extracted items included: article metadata (year of publication, author, journal), study characteristics (study location, data source, exposure, outcomes, diagnostic criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value). I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.

@@

Where additional data not reported by an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted. This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]

@@

A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis). To enable this triangulation exercise, detailed and structured risk-of-bias assessment formed an important part of this review.

@@

This move was prompted by an unclear definition of methodological quality which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools. <!-- TODO CITATION NEEDED --> As part of this shift, the focus moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order. <!-- TODO CITATION NEEDED --> Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.  For example, a study may report on the efficacy of an intervention at six months and two years follow-up. In this case, the proportion of missing outcome data may not be an issue at six months but may introduce bias after two years of follow-up. In this case, assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.

@@

Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result. Acceptable judgements for each domain include: "low risk", "some concerns", "high risk". Each of the five domains contains a series of signaling questions or prompts which guide the user through the tool. Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.

@@

For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result. Similar to RoB 2, it has a number of signaling questions which inform the domain-level judgement, with acceptable judgements including “low”, “moderate”, “serious” and “critical”. In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial. Under this approach, the (rare) overall judgement of "low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.

While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed. Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level. The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS. Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.

@@

At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available. Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification. Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.

@@

In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level. This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.

@@

Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading). Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).

@@

I used a random-effects model in all meta-analyses.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$. The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of the variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$. Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:

@@

Results included in a meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot. Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate. Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]

@@

Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g. for example, highest vs lowest quartile). <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results? --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups. In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels. This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.

@@

I took a two-stage dose-response meta-analysis approach, where study-specific trends are estimated before being pooled across studies.[@greenland1992] To estimate within-study trends, a restricted cubic spline model was fitted within each study. This approach allows for a non-linear relationship between lipid levels and dementia, for example a U or J-shaped relationship, where low and high levels of a lipid fraction can have different effects versus the "normal" reference dose.[@durrleman1989;@liu2009] Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table). Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.

Restricted cubic spline models use "knots" to separate the data into subsets or "windows", in which the trend is modelled. Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]

@@

One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond. This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool. Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.

@@

* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and lipid-regulating agents.

* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies. Additionally, I have highlighted how this review will examine the impact the of including preprinted results, as enabled by the research tool presented in the previous chapter.

* In the following chapter, I present the results of this review, and detail how the identified evidence is used throughout the remainder of the thesis.
